\chapter{Methodology}
\label{chap:methodology}

This section covers the approach taken to answer the research questions and the different research methods used in this work to ensure quality.
\section{Research methodology}
\subsection{Research flow}
\input{figures/3-research-flow}
Figure \ref{fig:3-research-flow} shows a visualisation of how the identified problems in the literature motivated the research objectives, how the objectives were reached through the research process and how the thesis documents the process and results.

The research started with an initial literature review in order to identify gaps or problems in the literature. The results of the review informed the research objectives. 
The literature review was continued after the objectives were identified and progressed alongside with the other research activities. The other research activities that were done was a survey, model proposition and expert evaluation. The survey was conducted to better understand the use of \gls{ea} in a smart city project context, how the +CityxChange \gls{eaf} in particular contributed to the project and how it and \gls{ea} in general related to +CityxChange's learning efforts.
The survey was implemented using an online questionnaire.
The data gathered from the survey was used with the data from the literature review in order to identify the requirements and to propose a model consisting of an \gls{eaf}, a development process and \gls{ea} elements. An \gls{ea} element is considered as a visual representation of an uninstantiated entity that can be used in an \gls{ea} model. When the element is instantiated it becomes a component. 
The model was evaluated with an expert evaluation, using semi-structured interviews. 

\subsection{Literature Review approach}
\input{tables/screeningQuestions}
\iffalse\input{figures/screeningProcess} \fi
\begin{itemize}
    \item \textbf{Query construction:} Literature was queried using the search engines at google scholar, web of science, Scopus and Oria. The search terms used included: "Enterprise Architecture" AND "smart cities", Learning from "Enterprise Architecture models", cities as learning innovation ecosystems, and knowledge transfer across cities. Additional literature was gathered based on references and authors.
    
    \item \textbf{Screening:} Relevance and quality was assessed to exclude articles given by the query. The questions used to assess quality and relevance are listed in table \ref{tab:sceeningQuestions}. \iffalse and the result of the query and screening is displayed in figure \ref{fig:screening}. \fi
    
\end{itemize}

\subsection{Survey approach}
\begin{itemize}
    \item \textbf{Data collection method:} A questionnaire was used to gather data. The questions were based on the initial literature review discussed in chapter \ref{chap:literature} and based on the \gls{tam} to indicate potential of the \gls{eaf} proposed in +CityxChange.
    The questionnaire was made primarily for this thesis, but also to be used for a delivery within +CityxChange project \cite{cityxchange-d1.2}. As a result not all questions of the questionnaire were deemed relevant for this thesis. The questionnaire consisted of 6 parts; information about the questionnaire and consent to use and publish data, demographic on participants, view of \gls{ea} in general, view of \gls{eaf} used in +CityxChange, view of how \gls{ea} in general and the \gls{eaf} in particular relates to knowledge transfer and a final section for free-text answers with the opportunity to give feedback that the participants felt were missing or required clarification.
    In total there were 47 questions and the questions were given via nettskjema.no due to an existing data processing agreement with \gls{ntnu}. Permission to process personal data was granted by the \gls{nsd} and all participant consented to the use of relevant data.
    \item \textbf{Population/sampling:}
    The questionnaire was given online to 42 participants with a connection to +CityxChange. The criteria for receiving the questionnaire was a familiarity with the \gls{eaf} used in +CityxChange. Of the 42 asked participants 13 participated. A question within the questionnaire asked for their familiarity with the \gls{eaf} on which one participant indicated that they were not familiar with the \gls{eaf}. Although this indicate that this person did not fit the criteria for receiving and answering the questionnaire, the answers were still included in the analysis. 
    \item \textbf{Data analysis:} Due to the limited number of answers, a qualitative approach were used for most questions including all free-text questions. Percentages and graphics were calculated and created by nettskjema. 
    \iffalse Analysis was conducted using \gls{spss}. \fi
\end{itemize}

\subsection{Model proposition approach}    
The model proposition followed a designed and creation process with five steps
\begin{itemize}
    \item \textbf{Awareness:} The needs of the model were gathered through the literature review and questionnaire.
    \item \textbf{Suggestion:} A potential solution to the needs were suggested.
    \item \textbf{Development:} A model implementing the suggestions were developed.
    \item \textbf{Evaluation:} The model was evaluated with expert evaluation
    \item \textbf{Conclusion:} The results were analysed and reported in this thesis.
\end{itemize}

\subsection{Expert evaluation approach}
\input{tables/4-evaluation-interview}
\begin{itemize}
    \item \textbf{Data collection method:} A semi structured interview was used for the evaluation. The interview consisted of six themes; "Role of \gls{ea}", "Participation,  Malleability, annotation and shared syntax", "Visualization, Accessibility", "+CityxChange, concreteness", "Modularity", "Technology acceptance". The themes and relevant questions are listed in table \ref{tab:4-evaluation-interview}. The themes are based on the \gls{boundary object} discussed in \cite{abraham2015crossing} and \gls{tam}. 12 questions were prepared before the interview and used to guide the interview. 30 minutes were allocated to each interview as the participants were busy and requested that it be kept short. Not all questions were asked during every interview due to the time constraint and nature of semi structured interviews. The themes were still covered. The interviewees were given a short introduction to the proposed model consisting of the proposed \gls{eaf}, development process and \gls{ea} elements, but were not given definitions of the layers or use case for the elements, unless explicitly requested. This was done to determine if the terminology used was appropriate and intuitive. Intuitiveness was one of the problems identified through the questionnaire and seen as important for the evaluation.
    \item \textbf{Population/sampling:} Three participants were selected and interviewed separately. All three were selected based on their knowledge of either the +CityxChange \gls{eaf} or learning within smart city projects.
    The qualities of the participants that were important for the sampling process were: 
    \begin{itemize}
        \item Participant 1: Experienced with \gls{ea} and one of the architects behind the \gls{eaf} used in +CityxChange.
        \item Participant 2: Familiar with \gls{ea} for smart cities and a contributor to the \gls{eaf} used in +CityxChange.
        \item Participant 3: Not familiar with \gls{ea}, but experienced with urban planning and learning across cities. 
    \end{itemize}
\end{itemize}