\chapter{+CityxChange EAF evaluation}
This chapter presents an evaluation of the +CityxChange based on the literature review and information gathered from +CityxChange. 

\section{Evaluation based on data gathered from +CityxChange}
The evaluation presented in this section is informed by the survey presented in chapter \ref{chap:survey} and meeting notes. The meeting notes were taken during meetings between \gls{ea} architect and key personnel with an overview of the +CityxChange. The meetings were conducted to give feedback and correct deviations between \gls{ea} models created using the +CityxChange \gls{eaf} and their \gls{ict ecosystem}. 

\begin{itemize}[label=+]
    \item Its focus is relevant for the information that needs to be transferred.
    \item Goals and interests can be shown.
    \item Separate view can be used to mask information that is not important to individuals.
    \item External factors are considered.
    \item The representation covers the necessary parts of the system for development. 
\end{itemize}
\begin{itemize}[label=-]
    \item It is too complicated for beginners.
    \item The framework presentation can be confusing.
    \item The terminology can be confusing.
    \item The term "Business" has been criticised as being inappropriate when citizen welfare is a core motivator. 
    \item It is not designed with specific knowledge retention or knowledge sharing activities or methods in mind. 
    \item The focus is on the \gls{ict} system modelling and not on the human aspect.
\end{itemize}

\section{Evaluation based on Boundary objects perspective from literature}
The evaluation presented here is based on the \glspl{boundary object} properties described in \cite{abraham2015crossing};
\begin{itemize}
    \item \textbf{Accessibility:} The questionnaire indicate that complexity made it inappropriate as a communication channel with other communities than those experienced with \gls{ea}.  
    \item \textbf{Concreteness:} The questionnaire indicated that there was no information missing from the model that was desired by the respondents.  
    \item \textbf{Modularity:} The models layered architecture allow for high modularity.
    \item \textbf{Shared syntax:} Multiple respondents to the questionnaire requested revisiting the terminology, indicating that the syntax is flawed.
    \item \textbf{Annotation:} The model does not specifically encourage nor discourage annotation.
    \item \textbf{Visualization:} The current use of the model uses standard notations for \gls{togaf}. The representation of the \gls{eaf} itself has been noted as confusing. 
    \item \textbf{Malleability:} The complexity of the \gls{eaf} might prevent changes of the models without help of an \gls{ea} architect. 
    \item \textbf{Participation:} The meetings used to inform the model involved multiple communities, but the complexity of the \gls{eaf} might prevent direct change by the communities. 
    \item \textbf{Up-to-Dateness:} The \gls{eaf} does not specifically encourage nor discourage continuous change.   
\end{itemize}

\section{Evaluation based on Innovation perspective from literature}
The evaluation presented here is based on the innovation capabilities described in \cite{louw2017architecting}.
\input{tables/4-innovation-capabilities}
Table \ref{tab:4-innovation-capabilities} shows an attempt at mapping the innovation capabilities to the +CityxChange \gls{eaf}. Not all capabilities had a clear connection to each layer, therefore they were altered slightly and mapped to the best fit. Some of the capabilities could fit into multiple layers, showing that there might be an unintended overlap between the layers. Other capabilities did not fit well into any layer and where added to the closest layer based on terminology. This was often the case with capabilities surrounding procedures. Some of these procedures had clear ties to data, but did not fit into the data perspective or data layer while other related to policies. Many of the procedures that did not have a clear mapping was added to the context layer as that seemed to be the best fit. 

The mapping indicates that procedures are an important aspect of enterprises and innovation or learning, and are not explicitly covered by the \gls{eaf}. The mapping also indicate that the context layer is overworked. 