{\centering
\begin{longtable}{|p{2.3cm}|p{4.5cm}|p{5cm}|}
    \hline
        Themes & Questions & Motivation\\ \hline
        \multirow{1}{2.3cm}{Role of \gls{ea}} 
            & \multirow{2}{4.5cm}{First off, I would like to know a bit about how you view \gls{ea} as a whole. So, What do you consider to be the job of \gls{ea}?} & Lead off with a question the participant is likely to already have an opinion on. \\ \cline{3-3}
            & & Understand whether or not the proposed model is aligned with the needs of the participant. \\
        \hline
        \multirow{3}{2.3cm}{Participation,  Malleability, annotation and shared syntax} 
            & \multirow{2}{4.5cm}{Who do you think has a use for the \gls{ea} models?} & Understand the usage context. \\ \cline{3-3}
            & & Understand if the \gls{eaf} is aligned with the users needs. \\ \cline{2-3}
            & \multirow{1}{4.5cm}{Do you think the suggested \gls{eaf} allow them (groups of users) to adequate model their perspective of the \gls{ea}? (Why, why not?)} & Understand if it supports the different usage contexts \\ \cline{3-3}
            & & Understand if there are perspectives with misssing elements. \\ \cline{2-3}
            & \multirow{2}{4.5cm}{Do you think that any part of the \gls{eaf} could be interpreted differently by some of the users? (Why, why not?)} & Understand if the users would have a common understanding of the resulting model. \\ \cline{3-3}
            & & Understand if the syntax or terminology has contradictory meanings within between different communities. \\
        \hline
        \multirow{2}{2.3cm}{Visualization, Accessibility} 
            & \multirow{1}{4.5cm}{Do you think the \gls{eaf} would give an efficient representation of the \gls{ea}? (why, why not)} & Understand whether or not the visualization is easy to interpret and important components can quickly be identified. \\ \cline{2-3}
            & \multirow{1}{4.5cm}{Do you think the \gls{eaf} will be understood by non-practitioners of \gls{ea}? (why, why not)} & Understand if the complexity is too high or if it creates problems when using the model to introduce the \gls{ea} to new personnel. \\
        \hline
        \multirow{2}{2.3cm}{+CityxChange, concreteness} 
            & \multirow{1}{4.5cm}{Do you think the \gls{eaf} is adequate for +CityxChange projects? (why, why not)} & Understand if the needs of +CityxChange is aligned with the \gls{eaf}. \\ \cline{2-3}
            & \multirow{1}{4.5cm}{Is there anything you think is unnecessary in the \gls{eaf}? (why, why not)} & Understand whether or not the \gls{eaf} is to broad or can be simplified without negative effects. \\
        \hline
        \multirow{1}{2.3cm}{Modularity} 
            & \multirow{2}{4.5cm}{Would the \gls{eaf} allow specific problems to be viewed separately from the entire \gls{ea} while maintaining correctness or validity? (why, why not) } & Understand if the \gls{eaf} supports modularity. \\ \cline{3-3}
            & & Understand if the different users of the model can work on what is relevant to them without unnecessary interference. \\
        \hline
        \multirow{3}{2.3cm}{Technology acceptance} 
            & \multirow{1}{4.5cm}{Do you think the \gls{eaf} would be usefull for +CityxChange or smart city development?} & Understand "perceived usefulness" as it relates to \gls{tam} and +CityxChange and the smart city development projects. \\ \cline{2-3}
            & \multirow{1}{4.5cm}{Do you think the \gls{eaf} would be easy to use?} & Understand "perceived ease of use" as it relates to \gls{tam}. \\ \cline{2-3}
            & \multirow{1}{4.5cm}{Would you use this yourself or recommend it to others?} & Understand "intent to use" as it relates to \gls{tam}. \\
    \hline
    
    \caption{Interview questions for expert evaluation of proposed EAF}
    \label{tab:4-evaluation-interview}
\end{longtable}}