{\centering
\begin{longtable}{|p{6cm}|p{6cm}|}
    \hline
    Mindset & Relevant \gls{boundary object} properties \\ \hline
    Why is the model needed? & concreteness\\ \hline
    Who is the model for? & concreteness, malleability, participation \\ \hline

    What is relevant for the models users? & concreteness, malleability, participation\\ \hline
    What is needed to make decisions? & concreteness \\ \hline
    How does the \gls{ea} look to outsiders? & concreteness\\ \hline

    Where can users find more information? & concreteness, (indirect) accessibility \\ \hline
    What documentation needs to be updated on changes? &  Up-to-dateness \\ \hline

    Who and what is communicated? & concreteness \\ \hline
    Which protocols or processes do they use? & concreteness \\ \hline
    Which techniques are used to share/retain knowledge? & concreteness \\ \hline
    How is communication documented? & concreteness\\ \hline

    Who has an interest in the systems completion? & concreteness, malleability, participation \\ \hline
    Who participates in development? & concreteness, malleability, participation \\ \hline

    Do groups interpret the system differently? & shared syntax, annotation, modularity\\ \hline
    Do groups have different terminology? & shared syntax \\ \hline
    Are there things that are likely to be misinterpreted? & shared syntax \\ \hline
    Can unnecessary information be hidden? & modularity, visualization\\ \hline
    
    Have human resources been allocated? & concreteness \\ \hline
    Have financial resources been allocated? & concreteness, visualization \\ \hline
    Are there missing resources? & concreteness, visualization \\ \hline
    Could resources improve the system? & concreteness, visualization \\ \hline
    
    \caption{A mapping of the mindsets to relevant Boundary object properties}
    \label{tab:4-mindset-properties}
\end{longtable}}